---
title: "Check performance of the new ctree and cforest using OpenML"
author: "Heidi Seibold"
# output: html_document
output: pdf_document
---

```{r setup, include=FALSE}
library("knitr")
opts_chunk$set(message = FALSE)
library("ggplot2")
library("OpenML")
```




# Classification tasks

```{r, echo=FALSE}
load(file = "grid_classif.rda")
```
```{r}
grid_classif
```

## Collect all information
```{r}
eval_classif <- listOMLRunEvaluations(run.id = grid_classif$run.id)

runeval_classif <- cbind(grid_classif, eval_classif)
```

## Visualise
```{r, fig.height=3, fig.width=7, out.width='900px'}
ggplot(runeval_classif, aes(x = parameter, color = data.name, group = interaction(data.name, type), linetype = type)) +
  geom_point(aes(y = predictive.accuracy)) + geom_line(aes(y = predictive.accuracy))
```




-------------------------------------



# Regression tasks

```{r, echo=FALSE}
load(file = "grid_regr.rda")
```
```{r}
grid_regr
```

## Collect all information
```{r}
eval_regr <- listOMLRunEvaluations(run.id = grid_regr$run.id)

runeval_regr <- cbind(grid_regr, eval_regr)
```

## Visualise
```{r, fig.height=3, fig.width=7, out.width='900px'}
ggplot(runeval_regr, aes(x = parameter, color = data.name, group = interaction(data.name, type), linetype = type)) +
  geom_point(aes(y = mean.absolute.error)) + geom_line(aes(y = mean.absolute.error))
```




--------------------------------


# Papers

Casalicchio, G., Bossek, J., Lang, M., Kirchhoff, D., Kerschke, P., Hofner, B., Seibold, H., Vanschoren, J., Bischl, B. (2017).   
**OpenML: An R Package to Connect to the Networked Machine Learning Platform OpenML.**   
*ArXiv e-prints*, [arxiv.org/abs/1701.01293](https://arxiv.org/abs/1701.01293).
 
Vanschoren, J., Van Rijn, J. N., Bischl, B., Torgo, L. (2014).    
**OpenML: networked science in machine learning.**   
*ACM SIGKDD Explorations Newsletter*, 15(2), 49-60, 
[doi:10.1145/2641190.2641198](https://doi.org/10.1145/2641190.2641198).
