---
title: "Test the new ctree on OpenML"
author: "Heidi Seibold"
# output: html_document
output: pdf_document
---


```{r setup, include=FALSE}
library("knitr")

## check if all chunks need to run or if this has happened already
run_classif_all <- !file.exists("runs.rda")
run_regr_all <- !file.exists("runs_regr.rda")

flow_descr <- "Please use the mlr add-on code https://github.com/HeidiSeibold/sandbox/blob/master/rstuff/openml_newctree/new_ctree_mlr.R
and devel partykit package revision 1089: https://r-forge.r-project.org/scm/viewvc.php/pkg/devel/?root=partykit"

opts_chunk$set(message = FALSE, cache = TRUE)
library("OpenML")
source("https://raw.githubusercontent.com/HeidiSeibold/sandbox/master/rstuff/openml_newctree/new_ctree_mlr.R")
```



# Study the behaviour of an algorithm on many different data sets

- New implementation of ``ctree()`` and ``cforest()``.
- Check performance with respect to 
    + **predictive accurancy** (percentage of instances that are classified 
      correctly) for classification tasks
    + **root mean squared error** for regression tasks


## Steps
- Create the flow
- Download the tasks
- Create runs (run flows on tasks)
- Upload runs
- Collect all information
- Visualise

Parameters to check:
```{r}
parms_ctree <- list(default = list(),
                    # splittest = list(splittest = TRUE, testtype = "MonteCarlo", nresample = 500),
                    lookahead = list(lookahead = TRUE),
                    # MIA = list(MIA = TRUE),
                    multiway = list(multiway = TRUE),
                    intersplit = list(intersplit = TRUE),
                    nmax = list(nmax = 20))
str(parms_ctree)

## add traceing for forest
parms_cforest <- lapply(parms_ctree, function(x) {
  x$trace <- TRUE
  return(x)
  })
```


# Classification tasks

## Create the flow
- [Implement algorithm](https://github.com/HeidiSeibold/sandbox/blob/master/rstuff/openml_newctree/new_ctree_mlr.R) 
  in ``mlr`` (see [mlr tutorial](http://mlr-org.github.io/mlr-tutorial/devel/html/create_learner/index.html)).
- create learners




ctree:
```{r}
lrn_list_ctree_classif <- lapply(parms_ctree, function(p) {
  makeLearner("classif.develpartykit.ctree", par.vals = p)
})
```

cforest:
```{r}
lrn_list_cforest_classif <- lapply(parms_cforest, function(p) {
  makeLearner("classif.develpartykit.cforest", par.vals = p,
              config = list(on.par.without.desc = "quiet"))
})
```


- create OMLFlow and [upload](http://www.openml.org/f/5439)
```{r, eval = run_classif_all}
flow <- convertMlrLearnerToOMLFlow(lrn_list_ctree_classif[[1]])
flow$description <- flow_descr
uploadOMLFlow(flow)
```

```{r, eval = run_classif_all}
flow <- convertMlrLearnerToOMLFlow(lrn_list_cforest_classif[[1]])
flow$description <- flow_descr
uploadOMLFlow(flow)
```


## Download the relevant tasks
- Select relevant tasks
```{r}
taskinfo_classif0 <- listOMLTasks(task.type = "Supervised Classification",
                          evaluation.measures = "predictive_accuracy",
                          number.of.instances = c(80, 10^6),
                          number.of.classes = c(2, 10), 
                          number.of.features = c(3, 50),
                          number.of.missing.values = c(1, 10^6),
                          estimation.procedure = "10-fold Crossvalidation")
taskinfo_classif1 <- taskinfo_classif0[taskinfo_classif0$max.nominal.att.distinct.values < 10, ]

set.seed(100) 
taskinfo_classif <- taskinfo_classif1[sample(seq_len(NROW(taskinfo_classif1)), size = 2), ]
```
- Download tasks
```{r}
tid <- taskinfo_classif$task.id
tasks <- lapply(tid, getOMLTask)
names(tasks) <- tid
```

----
```{r, echo=FALSE}
kable(taskinfo_classif[, c("name", "number.of.instances", "number.of.classes",
                   "number.of.features", "number.of.missing.values")],
      row.names = FALSE)
```



## Create runs (run flows on tasks)
- Set up grid to run each learner on each task
```{r}
grid_classif <- expand.grid(task.id = taskinfo_classif$task.id, parameter = names(parms_ctree))
```

- Run learners on tasks
```{r, eval=run_classif_all}
run_ctree_classif <- function(i) {
  print(i)
  runTaskMlr(task = tasks[[as.character(grid_classif$task.id[i])]],
             learner = lrn_list_ctree_classif[[grid_classif$parameter[i]]])
}

runs_ctree_classif <- lapply(seq_row(grid_classif), run_ctree_classif)

# library("parallel")
# ncores <- detectCores() - 1
# runs_ctree_classif <- mclapply(seq_row(grid_classif), run_ctree_classif, mc.cores = ncores)
save(runs_ctree_classif, file = "runs_ctree_classif.rda")
```

```{r, eval=run_classif_all}
run_cforest_classif <- function(i) {
  print(i)
  runTaskMlr(task = tasks[[as.character(grid_classif$task.id[i])]],
             learner = lrn_list_cforest_classif[[grid_classif$parameter[i]]])
}

runs_cforest_classif <- lapply(seq_row(grid_classif), run_cforest_classif)

# library("parallel")
# ncores <- detectCores() - 1
# runs_cforest_classif <- mclapply(seq_row(grid_classif), run_cforest_classif, mc.cores = ncores)
save(runs_cforest_classif, file = "runs_cforest_classif.rda")
```


```{r, echo=FALSE}
load(file = "runs_ctree_classif.rda")
load(file = "runs_cforest_classif.rda")
```



## Upload runs
```{r, eval=run_classif_all}
run.id_ctree_classif <- lapply(runs_ctree_classif, uploadOMLRun, tags = "study_38", confirm.upload = FALSE)
grid_classif$run.id_ctree <- unlist(run.id_ctree_classif)
```
```{r, eval=run_classif_all}
run.id_cforest_classif <- lapply(runs_cforest_classif, uploadOMLRun, tags = "study_38", confirm.upload = FALSE)
grid_classif$run.id_cforest <- unlist(run.id_cforest_classif)
```
```{r, eval=run_classif_all}
save(grid_classif, file = "grid_classif.rda") 
```
```{r, echo=FALSE}
load(file = "grid_classif.rda")
```
```{r}
grid_classif
```

## Collect all information
```{r}
eval_ctree_classif <- listOMLRunEvaluations(run.id = grid_classif$run.id_ctree)
names(eval_ctree_classif) <- paste0(names(eval_ctree_classif), "_ctree")
eval_cforest_classif <- listOMLRunEvaluations(run.id = grid_classif$run.id_cforest)
names(eval_cforest_classif) <- paste0(names(eval_cforest_classif), "_cforest")

runeval_classif <- cbind(grid_classif,
                         eval_ctree_classif,
                         eval_cforest_classif)
```

## Visualise
```{r, fig.height=3, fig.width=7, out.width='900px'}
ggplot(runeval_classif, aes(x = parameter, color = data.name_ctree, group = data.name_ctree)) +
  geom_point(aes(y = predictive.accuracy_ctree)) + geom_line(aes(y = predictive.accuracy_ctree)) +
  geom_point(aes(y = predictive.accuracy_cforest)) + geom_line(aes(y = predictive.accuracy_cforest), linetype = 2)
```
Similar visualisation can be found on 
[openml.org/f/5434](http://www.openml.org/f/5458)








-------------------------------------




# Regression tasks

## Create the flow
- [Implement algorithm](https://github.com/HeidiSeibold/sandbox/blob/master/rstuff/openml_newctree/new_ctree_mlr.R) 
  in ``mlr`` (see [mlr tutorial](http://mlr-org.github.io/mlr-tutorial/devel/html/create_learner/index.html)).
- create learners

ctree:
```{r}
lrn_list_ctree_regr <- lapply(parms_ctree, function(p) {
  makeLearner("regr.develpartykit.ctree", par.vals = p)
})
```

cforest:
```{r}
lrn_list_cforest_regr <- lapply(parms_cforest, function(p) {
  makeLearner("regr.develpartykit.cforest", par.vals = p,
              config = list(on.par.without.desc = "quiet"))
})
```


- create OMLFlow and [upload](http://www.openml.org/f/5439)
```{r, eval = run_regr_all}
flow <- convertMlrLearnerToOMLFlow(lrn_list_ctree_regr[[1]])
flow$description <- flow_descr
uploadOMLFlow(flow)
```

```{r, eval = run_regr_all}
flow <- convertMlrLearnerToOMLFlow(lrn_list_cforest_regr[[1]])
flow$description <- flow_descr
uploadOMLFlow(flow)
```


## Download the relevant tasks
- Select relevant tasks
```{r}
taskinfo_regr0 <- listOMLTasks(task.type = "Supervised Regression",
                               evaluation.measures = "mean_absolute_error",
                               number.of.instances = c(80, 10^6),
                               number.of.features = c(3, 50),
                               number.of.missing.values = c(1, 10^6),
                               estimation.procedure = "10-fold Crossvalidation")
taskinfo_regr1 <- taskinfo_regr0[!is.na(taskinfo_regr0$max.nominal.att.distinct.values) &
                                   taskinfo_regr0$max.nominal.att.distinct.values < 10, ]
# taskinfo_regr1 <- taskinfo_regr0

set.seed(123) 
taskinfo_regr <- taskinfo_regr1[sample(seq_len(NROW(taskinfo_regr1)), size = 2), ]
```
- Download tasks
```{r}
tid_regr <- taskinfo_regr$task.id
tasks_regr <- lapply(tid_regr, getOMLTask)
names(tasks_regr) <- tid_regr
```

----
```{r, echo=FALSE}
kable(taskinfo_regr[, c("name", "number.of.instances", 
                   "number.of.features", "number.of.missing.values")],
      row.names = FALSE)
```



## Create runs (run flows on tasks)
- Set up grid to run each learner on each task
```{r}
grid_regr <- expand.grid(task.id = tid_regr, 
                         parameter = names(parms_ctree))
```
- Run learners on tasks
```{r, eval=run_classif_all}
run_ctree_regr <- function(i) {
  print(i)
  runTaskMlr(task = tasks_regr[[as.character(grid_regr$task.id[i])]],
             learner = lrn_list_ctree_regr[[grid_regr$parameter[i]]])
}

runs_ctree_regr <- lapply(seq_row(grid_regr), run_ctree_regr)

# library("parallel")
# ncores <- detectCores() - 1
# runs_regr <- mclapply(seq_row(grid_regr), run_regr_lt, mc.cores = ncores)
save(runs_ctree_regr, file = "runs_ctree_regr.rda")
```
```{r, eval=run_classif_all}
run_cforest_regr <- function(i) {
  print(i)
  runTaskMlr(task = tasks_regr[[as.character(grid_regr$task.id[i])]],
             learner = lrn_list_cforest_regr[[grid_regr$parameter[i]]])
}

runs_cforest_regr <- lapply(seq_row(grid_regr), run_cforest_regr)

# library("parallel")
# ncores <- detectCores() - 1
# runs_regr <- mclapply(seq_row(grid_regr), run_regr_lt, mc.cores = ncores)
save(runs_cforest_regr, file = "runs_cforest_regr.rda")
```


```{r, echo=FALSE}
load(file = "runs_ctree_regr.rda")
load(file = "runs_cforest_regr.rda")
```

## Upload runs
```{r, eval=run_regr_all}
run.id_ctree_regr <- lapply(runs_ctree_regr, uploadOMLRun, tags = "study_38", confirm.upload = FALSE)
grid_regr$run.id_ctree <- unlist(run.id_ctree_regr)
```
```{r, eval=run_regr_all}
run.id_cforest_regr <- lapply(runs_cforest_regr, uploadOMLRun, tags = "study_38", confirm.upload = FALSE)
grid_regr$run.id_cforest <- unlist(run.id_cforest_regr)
```
```{r, eval=run_regr_all}
save(grid_regr, file = "grid_regr.rda") 
```
```{r, echo=FALSE}
load(file = "grid_regr.rda")
```
```{r}
grid_regr
```

## Collect all information
```{r}
eval_ctree_regr <- listOMLRunEvaluations(run.id = grid_regr$run.id_ctree)
names(eval_ctree_regr) <- paste0(names(eval_ctree_regr), "_ctree")
eval_cforest_regr <- listOMLRunEvaluations(run.id = grid_regr$run.id_cforest)
names(eval_cforest_regr) <- paste0(names(eval_cforest_regr), "_cforest")

runeval_regr <- cbind(grid_regr,
                 eval_ctree_regr,
                 eval_cforest_regr)
```

## Visualise
```{r, fig.height=3, fig.width=7, out.width='900px'}
ggplot(runeval_regr, aes(x = parameter, color = data.name_ctree, group = data.name_ctree)) +
  geom_point(aes(y = predictive.accuracy_ctree)) + geom_line(aes(y = predictive.accuracy_ctree)) +
  geom_point(aes(y = predictive.accuracy_cforest)) + geom_line(aes(y = predictive.accuracy_cforest), linetype = 2)
```








# Papers

Casalicchio, G., Bossek, J., Lang, M., Kirchhoff, D., Kerschke, P., Hofner, B., Seibold, H., Vanschoren, J., Bischl, B. (2017).   
**OpenML: An R Package to Connect to the Networked Machine Learning Platform OpenML.**   
*ArXiv e-prints*, [arxiv.org/abs/1701.01293](https://arxiv.org/abs/1701.01293).
 
Vanschoren, J., Van Rijn, J. N., Bischl, B., Torgo, L. (2014).    
**OpenML: networked science in machine learning.**   
*ACM SIGKDD Explorations Newsletter*, 15(2), 49-60, 
[doi:10.1145/2641190.2641198](https://doi.org/10.1145/2641190.2641198).





