---
title: "Test the new ctree on OpenML"
author: "Heidi Seibold"
# output: html_document
output: pdf_document
---


```{r setup, include=FALSE}
library("knitr")

## check if all chunks need to run or if this has happened already
run_all <- !file.exists("runs.rda")
run_regr_all <- !file.exists("runs_regr.rda")

opts_chunk$set(message = FALSE, cache = TRUE)
library("OpenML")
source("https://raw.githubusercontent.com/HeidiSeibold/sandbox/master/rstuff/openml_newctree/new_ctree_mlr.R")
```



# Study the behaviour of an algorithm on many different data sets

- New implementation of ``ctree()``.
- Check performance with respect to 
    + **predictive accurancy** (percentage of instances that are classified 
      correctly) for classification tasks
    + **root mean squared error** for regression tasks


## Steps
- Create the flow
- Download the tasks
- Create runs (run flows on tasks)
- Upload runs
- Collect all information
- Visualise


# Classification tasks

## Create the flow
- [Implement algorithm](https://github.com/HeidiSeibold/sandbox/blob/master/rstuff/openml_newctree/new_ctree_mlr.R) 
  in ``mlr`` (see [mlr tutorial](http://mlr-org.github.io/mlr-tutorial/devel/html/create_learner/index.html)).
- create learners
```{r}
lrn.list <- list(
  makeLearner("classif.develpartykit.ctree"),
  makeLearner("classif.develpartykit.ctree", splittest = TRUE,
              testtype = "MonteCarlo", nresample = 1000),
  makeLearner("classif.develpartykit.ctree", lookahead = TRUE),
  # makeLearner("classif.develpartykit.ctree", MIA = TRUE),
  makeLearner("classif.develpartykit.ctree", multiway = TRUE),
  makeLearner("classif.develpartykit.ctree", intersplit = TRUE),
  makeLearner("classif.develpartykit.ctree", nmax = 20)
)

parameters <- sapply(lrn.list, function(x) names(x$par.vals[1]))
parameters[is.na(parameters)] <- "default"
parameters
names(lrn.list) <- parameters
```
- create OMLFlow and [upload](http://www.openml.org/f/5439)
```{r, eval = run_all}
flow <- convertMlrLearnerToOMLFlow(lrn.list[[1]])
flow$description <- "Please use the mlr add-on code https://github.com/HeidiSeibold/sandbox/blob/master/rstuff/openml_newctree/new_ctree_mlr.R and 
    devel partykit package revision 1082: https://r-forge.r-project.org/scm/viewvc.php/pkg/devel/?root=partykit"
uploadOMLFlow(flow)
```


## Download the relevant tasks
- Select relevant tasks
```{r}
taskinfo0 <- listOMLTasks(task.type = "Supervised Classification",
                          evaluation.measures = "predictive_accuracy",
                          number.of.instances = c(80, 10^6),
                          number.of.classes = c(2, 10), 
                          number.of.features = c(3, 50),
                          number.of.missing.values = c(1, 10^6),
                          estimation.procedure = "10-fold Crossvalidation")
taskinfo1 <- taskinfo0[taskinfo0$max.nominal.att.distinct.values < 10, ]

set.seed(1221) 
taskinfo <- taskinfo1[sample(seq_len(NROW(taskinfo1)), size = 4), ]


# set.seed(111) #Läuft unendlich problem
# taskinfo <- taskinfo0[sample(seq_len(NROW(taskinfo0)), size = 2), ]
```
- Download tasks
```{r}
tid <- taskinfo$task.id
tasks <- lapply(tid, getOMLTask)
names(tasks) <- tid
```

----
```{r, echo=FALSE}
kable(taskinfo[, c("name", "number.of.instances", "number.of.classes",
                   "number.of.features", "number.of.missing.values")],
      row.names = FALSE)
```



## Create runs (run flows on tasks)
- Set up grid to run each learner on each task
```{r}
grid <- expand.grid(task.id = taskinfo$task.id, parameter = parameters)
```
- Run learners on tasks
```{r, eval=run_all}
run_lt <- function(i) {
  print(i)
  runTaskMlr(task = tasks[[as.character(grid$task.id[i])]],
             learner = lrn.list[[grid$parameter[i]]])
}

runs <- lapply(seq_row(grid), run_lt)

# library("parallel")
# ncores <- detectCores() - 1
# runs <- mclapply(seq_row(grid), run_lt, mc.cores = ncores)
save(runs, file = "runs.rda")
```


```{r, echo=FALSE}
load(file = "runs.rda")
```



## Upload runs
```{r, eval=run_all}
run.id <- lapply(runs, uploadOMLRun, tags = "study_38", confirm.upload = FALSE)
grid$run.id <- unlist(run.id)
save(grid, file = "grid.rda") 
```
```{r, echo=FALSE}
load(file = "grid.rda")
```
```{r}
grid
```

## Collect all information
```{r}
runeval <- cbind(grid,
                 listOMLRunEvaluations(run.id = grid$run.id))
names(runeval)
```

## Visualise
```{r, fig.height=3, fig.width=7, out.width='900px'}
ggplot(runeval, aes(x = parameter, y = predictive.accuracy, 
                    color = data.name, group = data.name)) +
  geom_point() + geom_line()
```
Similar visualisation can be found on 
[openml.org/f/5434](http://www.openml.org/f/5458)




# Regression tasks

## Create the flow
- [Implement algorithm](https://github.com/HeidiSeibold/sandbox/blob/master/rstuff/openml_newctree/new_ctree_mlr.R) 
  in ``mlr`` (see [mlr tutorial](http://mlr-org.github.io/mlr-tutorial/devel/html/create_learner/index.html)).
- create learners
```{r}
lrn_regr.list <- list(
  makeLearner("regr.develpartykit.ctree"),
  makeLearner("regr.develpartykit.ctree", splittest = TRUE,
              testtype = "MonteCarlo", nresample = 1000),
  makeLearner("regr.develpartykit.ctree", lookahead = TRUE),
  # makeLearner("regr.develpartykit.ctree", MIA = TRUE),
  makeLearner("regr.develpartykit.ctree", multiway = TRUE),
  makeLearner("regr.develpartykit.ctree", intersplit = TRUE),
  makeLearner("regr.develpartykit.ctree", nmax = 20)
)

parameters_regr <- sapply(lrn_regr.list, function(x) names(x$par.vals[1]))
parameters_regr[is.na(parameters_regr)] <- "default"
parameters_regr
names(lrn_regr.list) <- parameters_regr
```
- create OMLFlow and [upload](http://www.openml.org/f/5439)
```{r, eval = run_regr_all}
flow_regr <- convertMlrLearnerToOMLFlow(lrn_regr.list[[1]])
flow_regr$description <- "Please use the mlr add-on code https://github.com/HeidiSeibold/sandbox/blob/master/rstuff/openml_newctree/new_ctree_mlr.R and 
    devel partykit package revision 1082: https://r-forge.r-project.org/scm/viewvc.php/pkg/devel/?root=partykit"
uploadOMLFlow(flow_regr)
```


## Download the relevant tasks
- Select relevant tasks
```{r}
taskinfo0_regr <- listOMLTasks(task.type = "Supervised Regression",
                               evaluation.measures = "mean_absolute_error",
                               number.of.instances = c(80, 10^6),
                               number.of.features = c(3, 50),
                               number.of.missing.values = c(1, 10^6),
                               estimation.procedure = "10-fold Crossvalidation")
# taskinfo1_regr <- taskinfo0_regr[!is.na(taskinfo0_regr$max.nominal.att.distinct.values) &
#                                    taskinfo0_regr$max.nominal.att.distinct.values < 10, ]
taskinfo1_regr <- taskinfo0_regr

set.seed(123) 
taskinfo_regr <- taskinfo1_regr[sample(seq_len(NROW(taskinfo1_regr)), size = 2), ]
```
- Download tasks
```{r}
tid_regr <- taskinfo_regr$task.id
tasks_regr <- lapply(tid_regr, function(x) try(getOMLTask(x)))
names(tasks_regr) <- tid_regr
```

----
```{r, echo=FALSE}
kable(taskinfo_regr[, c("name", "number.of.instances", 
                   "number.of.features", "number.of.missing.values")],
      row.names = FALSE)
```



## Create runs (run flows on tasks)
- Set up grid to run each learner on each task
```{r}
grid_regr <- expand.grid(task.id = tid_regr, 
                         parameter = parameters_regr)
```
- Run learners on tasks
```{r, eval=run_all}
run_regr_lt <- function(i) {
  print(i)
  runTaskMlr(task = tasks_regr[[as.character(grid_regr$task.id[i])]],
             learner = lrn_regr.list[[grid_regr$parameter[i]]])
}

runs_regr <- lapply(seq_row(grid_regr), run_regr_lt)

# library("parallel")
# ncores <- detectCores() - 1
# runs_regr <- mclapply(seq_row(grid_regr), run_regr_lt, mc.cores = ncores)
save(runs_regr, file = "runs_regr.rda")
```


```{r, echo=FALSE}
load(file = "runs_regr.rda")
```



## Upload runs
```{r, eval=run_all}
run_regr.id <- lapply(runs_regr, uploadOMLRun, tags = "study_38", confirm.upload = FALSE)
grid_regr$run.id <- unlist(run_regr.id)
save(grid_regr, file = "grid_regr.rda") 
```
```{r, echo=FALSE}
load(file = "grid_regr.rda")
```
```{r}
grid_regr
```

## Collect all information
```{r}
runeval_regr <- cbind(grid_regr,
                 listOMLRunEvaluations(run.id = grid_regr$run.id))
names(runeval_regr)
```

## Visualise
```{r, fig.height=3, fig.width=7, out.width='900px'}
ggplot(runeval_regr, aes(x = parameter, y = predictive.accuracy, 
                    color = data.name, group = data.name)) +
  geom_point() + geom_line()
```
Similar visualisation can be found on 
[openml.org/f/5434](http://www.openml.org/f/5434)








# Papers

Casalicchio, G., Bossek, J., Lang, M., Kirchhoff, D., Kerschke, P., Hofner, B., Seibold, H., Vanschoren, J., Bischl, B. (2017).   
**OpenML: An R Package to Connect to the Networked Machine Learning Platform OpenML.**   
*ArXiv e-prints*, [arxiv.org/abs/1701.01293](https://arxiv.org/abs/1701.01293).
 
Vanschoren, J., Van Rijn, J. N., Bischl, B., Torgo, L. (2014).    
**OpenML: networked science in machine learning.**   
*ACM SIGKDD Explorations Newsletter*, 15(2), 49-60, 
[doi:10.1145/2641190.2641198](https://doi.org/10.1145/2641190.2641198).





